An Airdrop That Preserves Recipient Privacy

### 2019-01-18 paper/paper.tex
edits

We design a ZKPK for a $\phi$-preimage 
using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
Here the verifier is given $T \in \GG^4 \times \ZZ$ 
and the prover is given $T$ and $\vv \in \ZZ^8$
where $\phi(\vv) = T$. 
The protocol works as follows:
\begin{enumerate}
\item The prover sets
    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
    \quad\text{and}\quad
   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2\lambda}}.
\]
The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
and sends $(c_1, c_2, \Rv)$ to the verifier.

@@

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\lnum \label{ln:randvell}
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randZ}
\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
\lnum \label{ln:sim}
\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover the quantities
$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
are chosen uniformly in $\range{N \cdot 2^{2\lambda}}$.
Consider one such value $r \rgets \range{N \cdot 2^{2\lambda}}$.
Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
we know that the pair
$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
Similarly,  in a real transcript
each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
each of these four values modulo $\ell$
is statistically close to uniform in $\range{\ell}$.
It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.

>>>>

We design a ZKPK for a $\phi$-preimage 
using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
Here the verifier is given $T \in \GG^4 \times \ZZ$ 
and the prover is given $T$ and $\vv \in \ZZ^8$
where $\phi(\vv) = T$. 
The protocol works as follows:
\begin{enumerate}
\item The prover sets
    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
    \quad\text{and}\quad
   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
\]
The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
and sends $(c_1, c_2, \Rv)$ to the verifier.

@@

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\lnum \label{ln:randvell}
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randZ}
\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
\lnum \label{ln:sim}
\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover the quantities
$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
are chosen uniformly in $\range{N}$.
Consider one such value $r \rgets \range{N}$.
Because $N$ is much larger than $\abs{\GG} \cdot \ell$
we know that the pair
$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
Similarly,  in a real transcript
each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
each of these four values modulo $\ell$
is statistically close to uniform in $\range{\ell}$.
It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
